Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Problem $\bm{\mathscr{C}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. The goal is to report, for each segment $h \in H$, the rightmost point $p$ on $h$ such that $p$ is covered by at least one left-end covering rectangle of $h$ in $R$ --- formally, for $h = [x_1, x_2] \times y$, we aim to find the maximum $x \in [x_1, x_2]$ such that at least one rectangle $r \in R$ covers both the point $(x_1, y)$ and the point $(x, y)$. If the point $p$ exists (i.e., $h$ has at least one left-end covering rectangle in $R$), we should output a tuple $(h, p)$; otherwise, output nothing for $h$. Figure~\ref{fig:probs}c gives an example where $H = \set{h_1, h_2}$ and $R$ includes the three rectangles shown; the output is $\set{(h_1, p_1), (h_2, p_2)}$. The problem can be solved in in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.

>>>>

\extraspacing {\bf Problem $\bm{\mathscr{C}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. The goal is to report, for each segment $h \in H$, the rightmost point $p$ on $h$ such that $p$ is covered by at least one left-end covering rectangle of $h$ in $R$ --- formally, for $h = [x_1, x_2] \times y$, we aim to find the maximum $x \in [x_1, x_2]$ such that at least one rectangle $r \in R$ covers both the point $(x_1, y)$ and the point $(x, y)$. If the point $p$ exists (i.e., $h$ has at least one left-end covering rectangle in $R$), we should output a tuple $(h, p)$; otherwise, output nothing for $h$. Figure~\ref{fig:probs}c gives an example where $H = \set{h_1, h_2, h_3}$ and $R$ includes the three rectangles shown; the output is $\set{(h_1, p_1), (h_2, p_2)}$. The problem can be solved in in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.
